\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{amsmath}
\geometry{a4paper, margin=1in}

% Configuring document structure
\title{Technical Guide for EduPath Career Tools}
\author{EduPath Development Team}
\date{May 15, 2025}

\begin{document}

\maketitle

\section*{Overview}
Detailing the technical architecture of the EduPath Career Tools platform.

\section{System Architecture}
Describing a client-side HTML/CSS/JavaScript application stored in localStorage.

\subsection{HTML Structure}
Utilizing semantic HTML5 elements (e.g., <header>, <main>, <section>) for accessibility.

\subsection{CSS Styling}
Applying responsive design with Flexbox and Grid, styled in career.css and calendar.css.

\subsection{JavaScript Logic}
Managing interactivity in career.js, skills.js, and notifications.js, using localStorage for data persistence.

\section{Key Features}
Implementing Job Matching, Resume Builder, Calendar, Notifications, and Accessibility.

\subsection{Data Storage}
Using localStorage with CLOUD_STORAGE_KEY "eduPathCareer" and "eduPathSkills".

\subsection{Event Handling}
Employing addEventListener for user interactions (e.g., button clicks, form submissions).

\section{Security Audit}
Conducting a simulated audit on May 15, 2025, at 06:10 PM +06.

\subsection{Identified Vulnerabilities}
\begin{itemize}
  \item \textbf{XSS Risk}: User input (e.g., resume-name) is directly inserted into HTML without sanitization.
  \item \textbf{LocalStorage Exposure}: Sensitive data (e.g., resume details) stored in plain text.
  \item \textbf{CSRF Risk}: No token validation for form submissions.
\end{itemize}

\subsection{Recommended Fixes}
\begin{itemize}
  \item Sanitize all user inputs using DOMPurify or similar libraries.
  \item Encrypt localStorage data with a client-side encryption library.
  \item Implement CSRF tokens for form submissions (server-side required).
\end{itemize}

\section{Deployment}
Hosting on a static server with HTTPS for security.

\end{document}