\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\geometry{a4paper, margin=1in}

\title{Test Analysis for EduPath Career Tools}
\author{EduPath Development Team}
\date{May 15, 2025}

\begin{document}

\maketitle

\section*{Test Overview}
Performing tests on May 15, 2025, at 06:29 PM +06, focusing on performance, usability, and security.

\subsection{Performance Test Results}
Measuring load time with simulated data.
\begin{itemize}
  \item Average Load Time: 1200ms (target < 1000ms).
  \item Critical Issue: Initial JS bundle size (200KB) impacts Time to Interactive.
\end{itemize}

\subsection{Usability Test Results}
Analyzing user interactions from interviews.
\begin{itemize}
  \item Success Rate: 85% for core tasks (e.g., job filtering, resume creation).
  \item Critical Issue: 15% of users missed form validation errors due to generic alerts.
  \item Critical Issue: Notification overlap affected 20% of users.
\end{itemize}

\subsection{Security Test Results}
Reassessing vulnerabilities from prior audit.
\begin{itemize}
  \item Critical Issue: XSS risk persists with unsanitized resume inputs.
  \item Critical Issue: LocalStorage data remains unencrypted.
\end{itemize}

\section{Critical Fixes}
\begin{itemize}
  \item Implement inline form validation with specific error messages.
  \item Add opt-in confirmation for browser notifications.
  \item Sanitize resume inputs to mitigate XSS.
  \item Encrypt localStorage data (requires library integration).
\end{itemize}

\section{Recommendations}
Optimizing JS bundle with further splitting, enhancing UI feedback, and conducting a full security review.

\end{document}