\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\geometry{a4paper, margin=1in}

\title{User Interviews for EduPath Career Tools}
\author{EduPath Research Team}
\date{May 15, 2025}

\begin{document}

\maketitle

\section*{Interview Summary}
Conducting interviews on May 15, 2025, at 06:29 PM +06 with three users.

\subsection{Participant 1: Alice, 25, Web Developer}
Evaluating usability of Job Matching and Resume Builder.
\begin{itemize}
  \item Positive: Appreciated lazy-loaded images and quick job filtering.
  \item Concern: Form validation alerts were unclear; suggested inline errors.
  \item Suggestion: Add a save button for resume drafts.
\end{itemize}

\subsection{Participant 2: Bob, 30, Data Analyst}
Testing Calendar and Notifications.
\begin{itemize}
  \item Positive: Liked reminder system flexibility.
  \item Concern: Browser notifications triggered unexpectedly; requested opt-in confirmation.
  \item Suggestion: Improve keyboard navigation feedback.
\end{itemize}

\subsection{Participant 3: Clara, 28, Designer}
Assessing Accessibility and Gamification.
\begin{itemize}
  \item Positive: Accessibility features (e.g., skip link) worked well with screen reader.
  \item Concern: Badge notifications overlapped with other content.
  \item Suggestion: Provide a tutorial for new users.
\end{itemize}

\section{Recommendations}
Incorporating inline form validation, opt-in confirmation for notifications, enhanced keyboard focus, and a user tutorial.

\end{document}