\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{amsmath}
\geometry{a4paper, margin=1in}

% Configuring document structure
\title{User Guide for EduPath Career Tools}
\author{EduPath Team}
\date{May 15, 2025}

\begin{document}

\maketitle

\section*{Introduction}
Welcoming users to the EduPath Career Tools platform, offering resources for career development.

\section{Getting Started}
Starting with accessing the platform via \href{https://edu.path}{edu.path}.

\subsection{Account Setup}
Creating an account by navigating to the homepage and selecting "Sign Up".

\subsection{Navigation}
Using the navigation menu to access Home, Courses, Career Tools, About, and Contact.

\section{Using Career Tools}
Exploring key features for career enhancement.

\subsection{Career Resource Center}
Accessing guides, skill assessments, and interview tips by clicking respective buttons.

\subsection{Job Matching}
Filtering jobs by category and level using dropdowns, then clicking "Search Jobs".

\subsection{Resume Builder}
Selecting a template, entering personal details, and generating a resume with the "Generate Resume" button.

\subsection{Calendar and Scheduling}
Adding tasks with task name, date, and time, adjusting deadlines, and setting reminders.

\subsection{Notifications}
Enabling browser notifications or email reminders via the Notification Preferences section.

\section{Troubleshooting}
Addressing common issues like form validation errors by filling all required fields.

\end{document}